% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Eduardo Gutarra}
% \address used twice to have two lines of address
\address{19603 Fernhaven, Katy, TX 77449}
\address{(281) 398-9692}

 
\begin{resume}

\section{OBJECTIVE} % (fold)
\label{sec:objective}
    Obtain a position as a SQL database developer or software engineer in a company. 
% section objective (end)

\section{EDUCATION} % (fold)
\label{sec:education}
    Research-based {\sl Master of Computer Science (MCS)} \\
    University of New Brunswick, Saint John, NB, Canada\\
    Thesis Title: Multi-column bitmap indexing\\
    Emphasis: Databases\\
    expected October 2011 \\\\
    {\sl Certification on Foundational CS Courses}--Industrial perspective \hfill Aug--Oct 2009\\
    Emphasis: .NET framework using C\#\\
    INFOSYS, Mysore, Karnataka, India\\\\
    {\sl Bachelor of Computer Science}\\
    EAFIT University \hfill Jun 2009\\
    Medell\a'in, Antioquia, Colombia\\
    G.P.A. 4.3/5.0\\
% section education (end)

\section{EXPERIENCE} % (fold)
\label{sec:experience}

{\sl Teaching Assistant} \hfill 2010--2011\\
Computer Science and Applied Statistics Department\\
University of New Brunswick, Saint John, NB, Canada
\begin{itemize} % \itemsep -2pt
    \item Assisted with instructional responsibilities for the following courses:
    \begin{itemize} \itemsep -2pt
        \item Introduction to Computer Programming in Matlab
        \item Introduction to Data Structures and Algorithms (C)
        \item Introduction to Computer Programming in Java
        \item Computer Science Concepts (Java)
    \end{itemize}
\end{itemize}

{\sl Software Engineer Intern} \hfill Jun 2008--Jan 2009\\
ION Geophysical, Houston, TX 77449
\begin{itemize} \itemsep -2pt
    \item Developed in C++ a command line utility for indexing trace header information.
    \item Performed research on MySQL storage engines.
    \item Deployed google-breakpad, a multi-platform crash reporting system.
\end{itemize}

{\sl Programmer/Analyst} \hfill 2007--2008\\
Biomecanica LTD, Medell\a'in, Colombia
\begin{itemize} \itemsep -2pt
    \item Designed and developed a clinical history report system for Biomecanica, using PHP and MySQL.
    \item Developed and tested back-up software using PHP and MySQL.
\end{itemize}

{\sl Teaching Assistant} \hfill 2007--May 2008\\
EAFIT University, Medell\a'in, Colombia
\begin{itemize} \itemsep -2pt
    \item  Assisted with instructional responsibilities for Compilers and Programming Fundamentals courses.
\end{itemize}

{\sl Web Developer} \hfill Summers  2004--2010\\
Panagro S.A., Medell\a'in, Colombia
\begin{itemize} \itemsep -2pt
    \item Designed and developed various web applications and web pages.  
    \item Programmed macros in Visual Basic for Excel worksheets.
\end{itemize}

% section experience (end)
 
\section{COMPUTER \\ SKILLS} % (fold)
\label{sec:computer_skills}
    {\sl Languages:}
    \begin{itemize} \itemsep -2pt
        \item Proficient in: C/C++, Java, C\#, Bash, Ruby, PHP
        \item Familiar with: Matlab
    \end{itemize}

    {\sl Software:}
    \begin{itemize} \itemsep -2pt
        \item Database: MySQL, SQL Server
        \item Operating Systems: MS Windows, Unix, OSX
        \item Design: Illustrator, Flash
    \end{itemize} 
% section computer_skills (end)

\section{ASSOCIATIONS} % (fold)
\label{sec:associations}
    Society of Exploration Geophysicists (SEG) \hfill 2008--Present\\
    Semillero de Investigaci\a'on de Recuperaci\a'on de Informaci\a'on (SIRI) \hfill 2007\\
% section associations (end)

\section{HONORS AND AWARDS} % (fold)
\label{sec:honors_and_awards}
    Top Performer of INFOSYS Training Program \hfill Oct 2009\\
    GEMIS Award for Undergraduate Project on Viper-SUGUI \hfill May 2009\\
% section honors_and_awards (end)

\section{LANGUAGES} % (fold)
\label{sec:languages}
    Fluent in Spanish (Read, Write, Speak)
% section languages (end)   

\end{resume}
\end{document}







